Safe Memory Regions for Big Data Processing

### 2016-06-02 paper/type-inference.tex
type inference

@@

The first step involves the following two mutually dependent ideas.

@@

\emph{Instantiation of Region Parametric Classes}. For every region
parametric class $\C{C}\langle \pi_0, \cdots, \pi_n \rangle$ so determined,
we replace every instance of class \C{C} in the program by an instance
$\C{C}\langle \rho_0, \cdots, \rho_n \rangle$, where $\rho_0, \cdots, \rho_n$
are fresh identifiers.

In particular, we determine the sequence of region parameters for a class \C{C}
by starting with the sequence of region parameters required for the type of
the base class of \C{C}, and adding fresh region parameters for the type of every field
in the class.
The class \C{Object} has a single region parameter $\pi_0$ (the allocation region).

>>>>

\paragraph{Terminology.}
In the sequel, we will be using \emph{region identifiers} in four different roles.
A region identifier may serve as
(a) A \emph{formal region parameter} of a class or method, or
(b) a \emph{static region identifier} introduced by a \C{letregion} construct, or
(c) an  \emph{open transferable region identifier} introduced by an \C{open} construct, or
(d) a \emph{region variable}, introduced to represent an unknown actual region parameter
of a method invocation or object alloation,
which will be bound to a region identifier of one of the three
preceding kinds by the end of the type inference.

@@

The first phase is an iterative process involving the following two
mutually dependent steps.

@@

\emph{Parameter Instantiation of Types}. For every region
parametric class $\C{C}\langle \pi_0, \cdots, \pi_n \rangle$ so determined,
we replace every instance of class \C{C} in the program by an instance
$\C{C}\langle \rho_0, \cdots, \rho_n \rangle$, where $\rho_0, \cdots, \rho_n$
are fresh identifiers.

We identify the region parameters of classes as follows.
The class \C{Object} is defined to have a single region parameter $\pi_0$ (the allocation region).
The region parameters for any other non-recursive class \C{C} is determined
only after the region parameters of any class that \C{C} depends on have been
determined: this includes the base-class \C{B} of \C{C} and the class (type)
of any of its fields.
We replace the type \C{T} of every field in \C{C} by its instantiated type,
using fresh region parameters as needed.
The sequence of region parameters for \C{C} is defined to be
the sequence of region parameters for the base class \C{B} concatenated
with the list of all  fresh region parameters introduced while instantiating the types
of the fields in the class.
